\textbf{Supplementary Information}

### 2020-03-12 submission/supplementary.Rmd
Manuscript 1st version complete.

\vspace{70mm}

^1$\dagger$^

@@

$\dagger$ To whom correspondence should be addressed: marino.korlevic@irb.hr

1\. Ruđer Bošković Institute, Center for Marine Research, G. Paliaga 5, Rovinj, Croatia

2\. University of Vienna, Department of Limnology and Bio-Oceanography, Althanstraße 14, Vienna, Austria

\linenumbers
\sisetup{mode=text}
\setlength\parindent{24pt}

## Supplementary Figures
```{r out.width="85%", fig.align="center", fig.cap="Rarefaction curves of bacterial and archaeal communities from the surfaces of macrophytes (\\textit{Cymodocea nodosa} [Invaded] and \\textit{Caulerpa cylindracea} [Invaded and Noninvaded]) and in the surrounding seawater.\\label{rarefaction}", fig.pos="H"}
include_graphics("../results/figures/rarefaction.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Seasonal dynamics of observed number of OTUs, Chao1, ACE, exponential of the Shannon Diversity Index and Inverse Simpson Index of bacterial and archaeal communities from the surfaces of macrophytes (\\textit{Cymodocea nodosa} [Invaded] and \\textit{Caulerpa cylindracea} [Invaded and Noninvaded]) and in the surrounding seawater.\\label{calculators}", fig.pos="H"}
include_graphics("../results/figures/calculators.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Relative contribution of chloroplast sequences on the surfaces of macrophytes (\\textit{Cymodocea nodosa} [Invaded] and \\textit{Caulerpa cylindracea} [Invaded and Noninvaded]) and in the surrounding seawater.\\label{chloroplast}", fig.pos="H"}
include_graphics("../results/figures/chloroplast_bar_plot.jpg")
```

>>>>

\vspace{60mm}
Marino Korlević^1$*$^, Marsej Markovski^1^, Zihao Zhao^2^, Gerhard J. Herndl^2,3^, Mirjana Najdek^1^

@@

^$*$^To whom correspondence should be addressed: marino.korlevic@irb.hr

1\. Center for Marine Research, Ruđer Bošković Institute, Croatia

2\. Department of Functional and Evolutionary Ecology, University of Vienna, Austria

3\. Department of Marine Microbiology and Biogeochemistry, Royal Netherlands Institute for Sea Research, Utrecht University, The Netherlands

\sisetup{mode=text}
\setlength\parindent{24pt}

## Supplementary Figures

```{r out.width="85%", fig.align="center", fig.cap="Rarefaction curves of bacterial and archaeal communities from the surfaces of macrophytes (\\textit{C. nodosa} [Invaded] and \\textit{C. cylindracea} [Invaded and Noninvaded]) and in the ambient seawater.\\label{rarefaction}", fig.pos="H"}
include_graphics("../results/figures/rarefaction.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Seasonal dynamics of observed number of OTUs, Chao1, ACE, exponential of the Shannon Diversity Index and Inverse Simpson Index of bacterial and archaeal communities from the surfaces of macrophytes (\\textit{C. nodosa} [Invaded] and \\textit{C. cylindracea} [Invaded and Noninvaded]) and in the ambient seawater.\\label{calculators}", fig.pos="H"}
include_graphics("../results/figures/calculators.jpg")
```

```{r out.width="85%", fig.align="center", fig.cap="Relative contribution of chloroplast sequences on the surfaces of macrophytes (\\textit{C. nodosa} [Invaded] and \\textit{C. cylindracea} [Invaded and Noninvaded]) and in the ambient seawater.\\label{chloroplast}", fig.pos="H"}
include_graphics("../results/figures/chloroplast_bar_plot.jpg")
```

### 2020-03-12 submission/supplementary.tex
Manuscript 1st version complete.

\vspace{70mm}

\textsuperscript{1\(\dagger\)}

@@

\(\dagger\) To whom correspondence should be addressed:
\href{mailto:marino.korlevic@irb.hr}{\nolinkurl{marino.korlevic@irb.hr}}

1. Ruđer Bošković Institute, Center for Marine Research, G. Paliaga 5,
Rovinj, Croatia

2. University of Vienna, Department of Limnology and Bio-Oceanography,
Althanstraße 14, Vienna, Austria

\linenumbers
\sisetup{mode=text}
\setlength\parindent{24pt}

@@

\caption{Rarefaction curves of bacterial and archaeal communities from the surfaces of macrophytes (\textit{Cymodocea nodosa} [Invaded] and \textit{Caulerpa cylindracea} [Invaded and Noninvaded]) and in the surrounding seawater.\label{rarefaction}}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\caption{Seasonal dynamics of observed number of OTUs, Chao1, ACE, exponential of the Shannon Diversity Index and Inverse Simpson Index of bacterial and archaeal communities from the surfaces of macrophytes (\textit{Cymodocea nodosa} [Invaded] and \textit{Caulerpa cylindracea} [Invaded and Noninvaded]) and in the surrounding seawater.\label{calculators}}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{Relative contribution of chloroplast sequences on the surfaces of macrophytes (\textit{Cymodocea nodosa} [Invaded] and \textit{Caulerpa cylindracea} [Invaded and Noninvaded]) and in the surrounding seawater.\label{chloroplast}}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\begin{longtable}[t]{>{\centering\arraybackslash}p{6em}ccccc}

>>>>

\vspace{60mm}

Marino Korlević\textsuperscript{1\(*\)}, Marsej
Markovski\textsuperscript{1}, Zihao Zhao\textsuperscript{2}, Gerhard J.
Herndl\textsuperscript{2,3}, Mirjana Najdek\textsuperscript{1}

@@

\textsuperscript{\(*\)}To whom correspondence should be addressed:
\href{mailto:marino.korlevic@irb.hr}{\nolinkurl{marino.korlevic@irb.hr}}

1. Center for Marine Research, Ruđer Bošković Institute, Croatia

2. Department of Functional and Evolutionary Ecology, University of
Vienna, Austria

3. Department of Marine Microbiology and Biogeochemistry, Royal
Netherlands Institute for Sea Research, Utrecht University, The
Netherlands

\sisetup{mode=text}
\setlength\parindent{24pt}

@@

\caption{Rarefaction curves of bacterial and archaeal communities from the surfaces of macrophytes (\textit{C. nodosa} [Invaded] and \textit{C. cylindracea} [Invaded and Noninvaded]) and in the ambient seawater.\label{rarefaction}}\label{fig:unnamed-chunk-1}
\end{figure}

@@

\caption{Seasonal dynamics of observed number of OTUs, Chao1, ACE, exponential of the Shannon Diversity Index and Inverse Simpson Index of bacterial and archaeal communities from the surfaces of macrophytes (\textit{C. nodosa} [Invaded] and \textit{C. cylindracea} [Invaded and Noninvaded]) and in the ambient seawater.\label{calculators}}\label{fig:unnamed-chunk-2}
\end{figure}

@@

\caption{Relative contribution of chloroplast sequences on the surfaces of macrophytes (\textit{C. nodosa} [Invaded] and \textit{C. cylindracea} [Invaded and Noninvaded]) and in the ambient seawater.\label{chloroplast}}\label{fig:unnamed-chunk-3}
\end{figure}

@@

\begin{longtable}{>{\centering\arraybackslash}p{6em}ccccc}
